---
title: "proteinQuant Package Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{proteinQuant Package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(proteinQuant)
```


## Introduction

The `proteinQuant` package provides a facile method to process and calculate assay results from **BCA assay**, **Bradford assay**, and **UV standard curve** protein quantification methods. The package features functions that allow users to quickly go through necessary calculations and obtain useful graphics when processing assay/UV-vis data. Additionally, the package features sample data sets comprised of real experimental data collected through the listed methods. Through that, this package aims to assist researchers who have to quantify proteins through these methods regularly. 


### Typical Workflow

To begin, users can input the data for their standard curve into the appropriate standard curve function, either `assay_regression` or `UV280_regression`, to obtain a standard curve for concentration calculations. The user can then input the resulting regression equation to `AssayConc` in addition to the absorbance data for their protein sample(s) to quantify protein concentration in their samples. The regression line can also be graphed out with the corresponding standard curve graphing function, `assay_graphing_tool` or `UV_graphing_tool`. 

Alternatively, the user can use the wrapper function `assayAnalysis`, which calls all the functions in the correct order in one run. This function yields a shorter output but still incorporates all the necessary functions. 


### Loading the Data

The `proteinQuant` package includes absorbance data experimentally collected from the UV 280 method or the BCA and Bradford assays. Data was collected during BCH 253 Biochemistry I lab.

Sample data can be loaded directly after loading the package.

```{r}
# load individual dataset for each quantification
data("bca_bradford_bsa_standard_curve")
data("BCA_sample_data")
data("bradford_sample_data")
data("UV_bsa_standard_curve")
data("UV_sample_data")
```


### Working across Assays

Sample data included in `proteinQuant` were separated based on type (UV or assay, standard curve or sample data). Most sets contain `absorbance` data while some also include concentration information. Concentrations were recorded in $\mu g/mL$. 


### Calculating Standard Curves

This package contains functions that can calculate both linear (for UV280 methods) and polynomial (for the BCA/ Bradford Assays results) regression models. 

#### UV Method Regressions

A linear regression is the most appropriate for the UV 280 method. To run `UV280_regression`, the user needs to specify the names of the columns for `concentration` and `absorbance`, as shown in the example run below. The regression equation will be returned by the function. Argument `stats` allows the user to choose to see the regression equation as the output when set to `TRUE`, otherwise this function will not yield any visible output.

```{r}
sample_data <- UV_bsa_standard_curve

UV280_regression(data = sample_data, 
                 concentration = Concentration.ug.mL., 
                 absorbance = Absorbance, 
                 stats = TRUE)
```

#### Assay Regressions

Quadratic regression is the most appropriate approach to generate standard curves for both the BCA and Bradford assays. To run `assay_regression`, the user needs to specify the names of the columns for `concentration` and `absorbance`, as shown in the example run below. The regression equation will be returned by the function. Argument `stats` allows the user to choose to see the regression equation as the output when set to `TRUE`, otherwise this function will not yield any visible output.

```{r}
sample_data <- bca_bradford_bsa_standard_curve

assay_regression(data = sample_data, 
                 concentration = Concentration.ug.mL., 
                 absorbance = Bradford_Absorbance, 
                 stats = TRUE)
```


### Graphing Functions

Graphing functions `UV_graphing_tool` and `assay_graphing_tool` are included in `proteinQuant` and can be used to quickly generate standard curve graphs. The user needs to specify the appropriate column names for `concentration` and `absorbance`. 

An example run of `UV_graphing_tool` is included below: 

```{r}
sample_data <- UV_bsa_standard_curve

UV_graphing_tool(data = sample_data, 
                 concentration = Concentration.ug.mL., 
                 absorbance = Absorbance)
```


### Calculating Concentrations

`assayConc` can be used to quantify real protein concentrations after the standard curve regression is already established. The user needs to specify the appropriate column for `absorbance` and input the coefficients of the `regression` as a list. The function will return the calculated concentrations next to its corresponding absorbance. An example run of `assayConc` is shown below.

```{r}
sample_bradf_regression <- assay_regression(data = bca_bradford_bsa_standard_curve, 
                                            concentration = Concentration.ug.mL., 
                                            absorbance = Bradford_Absorbance)

assayConc(data = bradford_sample_data, 
          absorbance = Absorbance, 
          regression = sample_bradf_regression)
```

### Wrapper Function

The wrapper function `assayAnalysis` is set up to automatically call all the necessary functions to perform full protein quantification analysis. The user needs to specify the type of `assay`, the data set used for `stdcurve`, specific columns for `stdconc` and `stdabs`, protein `data` to be quantified, and the `absorbance` of the protein samples. Setting `stats = TRUE` allows users to see the regression equation in the output, otherwise only the calculated concentration (and corresponding absorbance) and the regression line graph will be shown in the output.

```{r}
assayAnalysis(
  assay = "Bradford",
  stdcurve = bca_bradford_bsa_standard_curve,
  stdconc = Concentration.ug.mL.,
  stdabs = Bradford_Absorbance,
  data = bradford_sample_data,
  absorbance = Absorbance,
  stats = TRUE
)
```



## Conclusion

The `proteinQuant` package provides useful tools to process protein absorbance data. The functions of this package cover the 3 most common protein quantification methods: UV 280 and the BCA and Bradford assays. The package is designed to streamline the data analysis process for biochemists in both academic research and pharmaceutical industry settings.


